%
% Base.tex
%
\renewcommand{\thisname}{Chart::Base}
\section{\thisname}
\name{\thisname}
\file{Base.pm}
\requires{GD, Carp, FileHandle}
\begin{Description}
\thisclass is the abstract superclass of classes \class{Chart::Bars},
\class{Chart::Composite}, \class{Chart::Direction},
\class{Chart::ErrorBars}, \class{Chart::HorizontalBars},
\class{Chart::Lines}, \class{Chart::LinesPoints},
\class{Chart::Mountain}, \class{Chart::Pareto}, \class{Chart::Pie},
\class{Chart::Points}, \class{Chart::Split}, and
\class{Chart::StackedBars}.

Class \thisclass provides all public methods and most of the
attributes of \chart objects.
\end{Description}

\begin{Constructor}
An object instance of class \class{Chart} can be created with the
constructor \methoduse{new()}:\index{Methods!new()}
\begin{SmallExample}
\$obj = Chart::\textit{Type}\deref new();\\
\$obj = Chart::\textit{Type}\deref new(\parameter{width}, \parameter{height});
\end{SmallExample}
\textit{Type} here denotes the type of chart that is to be returned,
\eg, \methoduse{Chart::Bars\deref new()} returns a bar chart.

If \methoduse{new()} is called without arguments, the constructor will
return an object of size 300\ensuremath{\times}400 pixels. If
\methoduse{new()} is called with two arguments, \parameter{width} and
\parameter{height}, it will return a \chart object of the desired
size.
\end{Constructor}


\Methods\label{methods}\noindent%
\methoduse{\$obj\deref add\_dataset(\parameter{@array})}{\index{Methods!add\_dataset()}}\\
\begin{MethDecl}{\$obj\deref add\_dataset(\parameter{\bs @array\_ref})}{add\_dataset()}
Adds a dataset to the object. The argument is an array or a reference to
an array. Generally, the first array added is interpreted as being the
$x$ tick labels. The subsequent arrays contain the data points. \Eg,
after the calls\\
\methoduse{\$obj\deref add\_dataset('Harry', 'Sally');}\\
\methoduse{\$obj\deref add\_dataset(5, 8);}\\
\chart will draw a picture with two bars and label them `Harry' and
`Sally'.

Some modules will operate slightly differently. Have a look at the
description of the specific subclass to get more information. Such
differences will also come up if you want to use the \texttt{xy\_plot}
option in order to create a $x$--$y$ graph.
\end{MethDecl}

\methoddecl{\$obj\deref add\_pt(\parameter{@array})}{add\_pt()}
\begin{MethDecl}{\$obj\deref add\_pt(\parameter{\bs @array\_ref})}{add\_pt()}
This is a different method for adding data to a
\chart object. The argument can be an array or a reference to an
array. If you use this method, \chart wants the complete data of
one data point, \ie, all the data that are associated with the same $x$
value specified first in this call. \Eg,\\
\methoduse{\$obj\deref add\_pt('Harry', 5);}\\
\methoduse{\$obj\deref add\_pt('Sally', 8);}\\
would create the same graph as the example for \methoduse{add\_dataset()} above.
\end{MethDecl}

\methoddecl{\$obj\deref add\_datafile("\parameter{filename}",   \textit{type})}{add\_datafile()}
\methoddecl{\$obj\deref add\_datafile(\parameter{\$filehandle}, \textit{type})}{add\_datafile()}
\begin{MethDecl}{\$obj\deref add\_datafile()}{add\_datafile()}
This method adds the contents of a complete data file to the chart object.
\textit{type} can be \literal{set} or \literal{pt}.
In the former case, \literal{set}, each line in the data file must
represent a complete data set (\emph{data series}). The values of the set
must be separated by whitespace. \Eg, the file contents could look like
this:
\begin{quote}
\texttt{Harry  Sally}\\
\texttt{3      8}\\
\texttt{2      1}
\end{quote}

If the argument is \literal{pt}, the lines of the file must look
analogous to the parameter arrays used by method \methoduse{add\_pt()}:
Each line includes all the values of one data point (\ie, all the $y$
values associated with the same $x$ value), also separated by
whitespace. \Eg:
\begin{quote}
\small
\texttt{Harry 3 2}\\
\texttt{Sally 8 1}
\end{quote}
\end{MethDecl}

\begin{MethDecl}{\$obj\deref get\_data()}{get\_data()}
If you want a copy of the data that have been added
so far, make a call to this method like so:\\
\methoduse{\$dataref = \$obj\deref get\_data();}\\[\itemabstand]
This will return a reference to an array of references to
datasets. For example, you can get the $x$ tick labels by:\\
\methoduse{@x\_labels = @\{\$dataref->[0]\};}
\end{MethDecl}

\begin{MethDecl}{\$obj\deref clear\_data()}{clear\_data()}
This is the method to remove all data that may have been entered until now.
\end{MethDecl}

\methoddecl{\$obj\deref set(\parameter{attribute$_1$} \fatcomma \parameter{value$_1$}, \ldots, \mbox{\parameter{attribute$_n$} \fatcomma \parameter{value$_n$}})}{set()}
\methoddecl{\$obj\deref set(\parameter{\%hash})}{set()}
\methoddecl{\$obj\deref set(\parameter{attribute1}, \parameter{value$_1$}, \ldots, \mbox{\parameter{attribute$_n$}, \parameter{value$_n$}})}{set()}
\begin{MethDecl}{\$obj\deref set(\parameter{@array})}{set()}
Use this method to change the attributes of the chart object.
\methoduse{set()} looks for a hash of keys and values or an array of
keys and values. \Eg,\\
\methoduse{\$obj\deref set('title' \fatcomma 'The title of the image');}\\
would set the title. This would do the same job:\\
\methoduse{\%hash = ('title' \fatcomma 'The title of the image');}\\
\methoduse{\$obj\deref set(\%hash);}
\end{MethDecl}

\methoddecl{\$obj\deref png("\parameter{filename}")}{png()}
\methoddecl{\$obj\deref png(\$\parameter{filehandle})}{png()}
\methoddecl{\$obj\deref png(\parameter{FILEHANDLE})}{png()}
\methoddecl{\$obj\deref png("\parameter{filename}", \parameter{\bs@data})}{png()}
\begin{MethDecl}{\$obj\deref png()}{png()}
This method creates a \textsc{png} file.
The file parameter can be a file name, a reference to a filehandle or a
filehandle itself. If the file does not exist, \chart will
create it for you. If there is already a file, \chart will
overwrite it. In case of an error, the file is not created.\\
You can also add data to a \chart object through its
\methoduse{png()} method. The \parameter{@data} array should contain
references to arrays of data, with the first array reference pointing
to an array of $x$ labels. \parameter{@data} might look like this:\\
\methoduse{@data = (['Harry', 'Sally'], [5, 8], [50, 80]);}\\
This would set up a graph with two datasets and three data points in
these sets.
\end{MethDecl}

\methoddecl{\$obj\deref jpeg("\parameter{filename}")}{jpeg()}
\methoddecl{\$obj\deref jpeg(\parameter{\$filehandle})}{jpeg()}
\methoddecl{\$obj\deref jpeg(\parameter{FILEHANDLE})}{jpeg()}
\methoddecl{\$obj\deref jpeg("\parameter{filename}", \bs@data)}{jpeg()}
\begin{MethDecl}{\$obj\deref jpeg()}{jpeg()}
This is the method to create \textsc{jpeg} files. It works analogously
to the \methoduse{png()} method.
\end{MethDecl}

\methoddecl{\$obj\deref cgi\_png()}{cgi\_png()}
\begin{MethDecl}{\$obj\deref cgi\_jpeg()}{cgi\_jpeg()}
With the \textsc{cgi} methods you can create dynamic images for your web
site. The \textsc{cgi} methods will print the chart along with the
appropriate \textsc{http} header to \textsc{stdout}, allowing you to
call chart-generating scripts directly from your \textsc{html} pages
(\eg, with a \literal{$\langle$img src="image.pl" /$\rangle$}
\textsc{html} tag).
\end{MethDecl}

\begin{MethDecl}{\$obj\deref imagemap\_dump()}{imagemap\_dump()}
\chart can also return pixel position information so that you can
create image maps from the files generated by \chart. Simply set the
\literal{imagemap} option to \literal{true} before you generate the
file, then at the end call the \methoduse{imagemap\_dump()} method to
retrieve the information. A structure will be returned almost identical
to the \parameter{@data} array described above to pass the data into \chart.

\methoduse{\$imagemap\_data = \$obj\deref imagemap\_dump();}

Instead of single data values, references to arrays of pixel information
are passed. For the classes \class{Chart::Bars},
\class{Chart::HorizontalBars}, \class{Chart::Pareto} and
\class{Chart::StackedBars}, the arrays will contain two $x$--$y$ pairs
(specifying the upper left and the lower right corner of the bar).
Compare to: \\
\methoduse{(\$x1,\$y1,\$x2,\$y2) = @\{\$imagemap\_data\deref [\$dataset][\$datapoint]\};}

For the classes \class{Chart::Lines}, \class{Chart::Points},
\class{Chart::LinesPoints} and \class{Chart::Split}, the arrays will
contain a single $x$--$y$ pair (specifying the center of the point).
Compare to:\\
\methoduse{(\$x, \$y) = @\{\$imagemap\_data\deref [\$dataset][\$datapoint]\};}

A few caveats apply here. First of all, \chart uses the GD module by
Lincoln Stein to draw lines, circles, strings, and so on. GD treats the
upper-left corner of the \textsc{png}/\textsc{jpeg} image as the
reference point, therefore, positive $y$ values are measured from the
top of the image, not from the bottom. Second, these values will mostly
contain long decimal values. GD, of course, has to truncate these to
integer pixel coordinates. In a worst-case scenario, this will result in
an error of one pixel on your imagemap. If this is really an issue, your
only option is to experiment with it, or to contact Lincoln Stein and
ask him. Third, please remember that the $0^{th}$ dataset will be empty,
since that is the place for the data point labels on the $x$ axis.
\end{MethDecl}


\Attributes\label{options}%
These are the options which take effect on most \chart types.
There are three different kinds of attributes:
\begin{itemize}
\item attributes expecting a number for value (\eg, the number of pixels),
\item attributes expecting a textual value (\eg, the title of the chart),
\item attributes expecting a Boolean value.
\end{itemize}

Before Version 2.5 of the module, the Boolean value \literal{true} was
represented by the string \texttt{'true'}, and the Boolean value
\literal{false} was represented by the string \texttt{'false'}. For all
other values, the Boolean value was not well-defined.
From version 2.5 onwards, the Boolean value \literal{true} may be
represented by any of \texttt{1}, \texttt{'t'} and \texttt{'true'},
where case does not matter.
From version 2.5 onwards, the Boolean value \literal{false} may be
represented by any of \texttt{0}, \texttt{'f'}, \texttt{'false'}, and
\texttt{undef}, where case does not matter. For all other values, the
Boolean value is again not well-defined. Note that this behaviour is
closer to the standard Perl way but is not identical, due to the need
for backward compatibility in this module.

\begin{AttrDecl}{transparent}
Makes the background of the image transparent if set to \literal{true}.
Useful for making web page images. However, it does not seem to work
for all browsers. Defaults to \literal{false}.
\end{AttrDecl}

\begin{AttrDecl}{png\_border}
Sets the number of pixels used as a border between the graph and the
edges of the image. Defaults to 10.
\end{AttrDecl}

\begin{AttrDecl}{graph\_border}
Sets the number of pixels used as a border between the title/labels and
the actual graph within the image. Defaults to 10.
\end{AttrDecl}

\begin{AttrDecl}{text\_space}
Sets the amount of space left on the sides of text, to make it more
readable. Defaults to 3.
\end{AttrDecl}

\begin{AttrDecl}{title}
Tells \chart what to use for the title of the graph. If empty, no title
is drawn. \literal{\bs\bs} is treated as a newline. If you want to use
normal quotation marks instead of single quotation marks, remember to
quote (\literal{\bs\bs\bs\bs}) to get a linebreak. Default is empty.
\end{AttrDecl}

\begin{AttrDecl}{sub\_title}
Writes a subtitle under the title in smaller letters.
\end{AttrDecl}

\begin{AttrDecl}{x\_label}
Tells \chart what text to use as a label for the $x$ axis. If empty, no
label is drawn. Default is undef.
\end{AttrDecl}

\attrdecl{y\_label}
\begin{AttrDecl}{y\_label2}
Tells \chart what kind of label should be used for the description of
the $y$ axis on the left or the right side accordingly. If empty, no
label is drawn.  Default is undef.
\end{AttrDecl}

\begin{AttrDecl}{legend}
Specifies the placement of the legend. Valid values are
\literal{left}, \literal{right}, \literal{top},
\literal{bottom}, and \literal{none}. Choosing \literal{none}
tells \chart not to draw a legend. Default is \literal{right}.
\end{AttrDecl}

\begin{AttrDecl}{legend\_labels}
Sets the values for the labels for the different datasets. Should be
assigned a reference to an array of labels. \Eg,\\
\methoduse{@labels = ('foo', 'bar')};\\
\methoduse{\$obj->set ('legend\_labels' \fatcomma \bs @labels);}\\
Default is empty, in which case \literal{Dataset 1},
\literal{Dataset 2}, etc. are used as labels.
\end{AttrDecl}

\begin{AttrDecl}{tick\_len}
Sets the length of the $x$ and $y$ ticks in pixels. Default is 4.
\end{AttrDecl}

\begin{AttrDecl}{x\_ticks}
Specifies how to draw the $x$ tick labels. Valid values are
\literal{normal}, \literal{staggered} (labels are drawn alternatingly
close to the axis and further away from it), and \literal{vertical}
(label texts are rotated 90 degrees counter-clockwise). Default is
\literal{normal}.
\end{AttrDecl}

\begin{AttrDecl}{y\_ticks}
The number of ticks to plot on the $y$ scale, including the end points.
\Eg, for a $y$ axis ranging from 0 to 50, with ticks every 10 units,
\attruse{y\_ticks} should have a value of 6.
\end{AttrDecl}

\begin{AttrDecl}{min\_y\_ticks}
Sets the minimum number of $y$ ticks to draw when generating the $y$
axis. Default is 6, minimum is 2.
\end{AttrDecl}

\begin{AttrDecl}{max\_y\_ticks}
Sets the maximum number of $y$ ticks to draw when generating the $y$
axis. Default is 100. This limit is used to avoid plotting an
unreasonably large number of ticks if non-round values are used for
\attruse{min\_val} and \attruse{max\_val}. The value for
\attruse{max\_y\_ticks} should be at least 5 times as large as
\attruse{min\_y\_ticks}.
\end{AttrDecl}

\attrdecl{min\_x\_ticks}
\begin{AttrDecl}{max\_x\_ticks}
These work similar to \attruse{max\_y\_ticks} and
\attruse{min\_y\_ticks}, respectively. Of course, this applies only to
$x$--$y$ plots.
\end{AttrDecl}

\begin{AttrDecl}{integer\_ticks\_only}
Specifies how to draw the $x$ and $y$ ticks: as floating point
(\literal{false}, \literal{0}) or as integer numbers
(\literal{true}, \literal{1}). If you want integer ticks, it may
be better to set the attribute \attruse{precision} to zero. Default:
\literal{false}
\end{AttrDecl}

\begin{AttrDecl}{skip\_int\_ticks}
If \attruse{integer\_ticks\_only} was set to \literal{true} the
labels and ticks for the $y$ axis will be drawn every $n^{th}$ tick.
(Note that in \class{Chart::HorizontalBars} the $y$ axis runs
horizontally.) Defaults to 1, \ie, no skipping.
\end{AttrDecl}

\begin{AttrDecl}{precision}
Sets the number of digits after the decimal point. Affects in most cases
the $y$ axis only. In $x$--$y$ plots also affects the $x$ axis, and in
pie charts the labels. Defaults to 3.
\end{AttrDecl}

\begin{AttrDecl}{max\_val}
Sets the maximum $y$ value on the graph, overriding normal autoscaling.
Does not work for \class{Chart::Split} charts. Default is undef.
\end{AttrDecl}

\begin{AttrDecl}{min\_val}
Sets the minimum $y$ value on the graph, overriding normal autoscaling.
Does not work for Split charts. Default is undef. Caution should be
used when setting \attruse{max\_val} and \attruse{min\_val} to
floating point or non-round numbers: The range must start and end on a
tick, ticks must have round-number intervals and must include round
numbers.\\
Example: Suppose your dataset has a range of 35\ldots 114
units. If you specify these values as \attruse{min\_val} and
\attruse{max\_val}, respectively, the $y$ axis will be plotted with 80
ticks, so one at every unit. Without specification of
\attruse{min\_val} and \attruse{max\_val}, the system would
autoscale the range to 30\ldots 120 with 10 ticks every 10 units. If
\attruse{min\_val} and \attruse{max\_val} are specified to excessive
precision, they may be overridden by the system, plotting a maximum
\attruse{max\_y\_ticks} ticks.
\end{AttrDecl}

\begin{AttrDecl}{include\_zero}
If \literal{true}, forces the $y$ axis to include zero even if it is
not in the dataset range. Default is \literal{false}. -- Note:
It is better to use this option than to set \attruse{min\_val}
if this is all you want to achieve.
\end{AttrDecl}

\begin{AttrDecl}{skip\_x\_ticks}
Sets the number of $x$ ticks and $x$ tick labels to skip. (\Ie, if
\attruse{skip\_x\_ticks} were set to 4, \chart would draw every
$4^{th}$ $x$ tick and $x$ tick label). Default is undef.
\end{AttrDecl}

\begin{AttrDecl}{custom\_x\_ticks}
This option allows you to specify exactly which $x$ ticks and $x$ tick
labels should be drawn. It should be assigned a reference to an array of
desired ticks. Just remember that we are counting from the $0^{th}$
element of the array. (\Eg, if \attruse{custom\_x\_ticks} is assigned
[0,3,4], then the $0^{th}$, $3^{rd}$, and $4^{th}$ $x$ ticks will be
displayed) This does not apply to \class{Chart::Split},
\class{Chart::HorizontalBars} and \class{Chart::Pie}.
\end{AttrDecl}

\begin{AttrDecl}{f\_x\_tick}
Needs a reference to a function which accepts the $x$ tick labels
generated by \parameter{\$data\deref [0]} as its argument. This function
should return a reformatted version of the label as a string. \Eg\\
\methoduse{\$obj\deref set ('f\_x\_tick' \fatcomma \bs\&formatter;})\\
An example for the formatter function: Assume that $x$ labels are
seconds since some event. The referenced function could be designed to
transform this number of seconds to hours, minutes and seconds.
\end{AttrDecl}

\begin{AttrDecl}{f\_y\_tick}
Similar to \attruse{f\_x\_tick}, but for $y$ labels.
\end{AttrDecl}

\begin{AttrDecl}{colors}
\label{colors}
This option lets you control the colors the chart will use. It takes a
reference to a hash. The hash should contain keys mapped to references
to arrays of \textsc{rgb} values. E.g.,\\
\methoduse{\$obj->set('colors' \fatcomma \{'background' \fatcomma [255,255,255]\});}\\
sets the background color to white (which is the default).\\
Another possibility is to use named colors like 'red', 'blue'. The possible
list of named colors can be found in chapter \ref{app:colors}, page \pageref{app:colors}.\\ 
Valid keys for this hash are
\begin{itemize}
\item \literal{background} (background color for the chart)
\item \literal{title} (color of the title)
\item \literal{text} (all the text in the chart)
\item \literal{x\_label} (color of the $x$ axis label)
\item \literal{y\_label} (color of the primary $y$ axis label)
\item \literal{y\_label2} (color of the secondary $y$ axis label)
\item \literal{grid\_lines} (color of the grid lines)
\item \literal{x\_grid\_lines} (color of the $x$ grid lines -- on $x$ axis ticks)
\item \literal{y\_grid\_lines} (color of the $y$ grid lines -- on primary $y$ axis ticks)
\item \literal{y2\_grid\_lines} (color of the y2 grid lines -- on secondary $y$ axis ticks)
\item \literal{dataset0} \ldots \literal{dataset63} (the different datasets)
\item \literal{misc} (everything else, \eg, ticks, box around the legend)
\end{itemize}

NB. For composite charts, there is a limit of eight datasets per
component. The colors for \literal{dataset8} through \literal{dataset15}
will be the same as those for \literal{dataset0} through
\literal{dataset7} for the second component chart.
\end{AttrDecl}

\begin{AttrDecl}{title\_font}
This option changes the font of the title line. The value must be a GD
font, \eg, \methoduse{GD::Font\deref Large}.
\end{AttrDecl}

\begin{AttrDecl}{label\_font}
This option changes the font of the labels. The value must be a GD font.
\end{AttrDecl}

\begin{AttrDecl}{legend\_font}
This option changes the font for the legend text. The value must be a
GD font.
\end{AttrDecl}

\begin{AttrDecl}{tick\_label\_font}
This option changes the font of the ticks. The value must be a GD font.
\end{AttrDecl}

\begin{AttrDecl}{grey\_background}
Puts a nice soft grey background on the actual data plot when set to
\literal{true}. This is a flag. If you set this flag to 'false' then you may
redefine the background color to a color you like. For further information see chapter \ref{colors}
on page \pageref{colors}. Default is \literal{true}.
\end{AttrDecl}

\begin{AttrDecl}{x\_grid\_lines}
Draws grid lines matching up to $x$ ticks if set to \literal{true}.
Default is \literal{false}.
\end{AttrDecl}

\begin{AttrDecl}{y\_grid\_lines}
Draws grid lines matching up to $y$ ticks if set to \literal{true}.
Default is \literal{false}.
\end{AttrDecl}

\begin{AttrDecl}{grid\_lines}
Draws grid lines matching up to $x$ and $y$ ticks if set to
\literal{true}. Default is \literal{false}.
\end{AttrDecl}

\begin{AttrDecl}{imagemap}
Lets \chart know that you are going to ask for information about the
placement of the data for use in creating an image map from the chart.
This information can be retrieved using the
\mbox{\methoduse{imagemap\_dump()}}
method. NB. The \methoduse{imagemap\_dump()} method cannot be called
until after the chart has been generated (\eg, using the \methoduse{png()}
or \methoduse{cgi\_png()} methods).
\end{AttrDecl}

\begin{AttrDecl}{ylabel2}
The label for the secondary (right-hand side) $y$ axis. (In a composite
chart, this is the axis for the second component). Default is undef.
\end{AttrDecl}

\begin{AttrDecl}{no\_cache}
Adds \literal{Pragma: no-cache} to the \textsc{http} header.
Be careful with this one, since some older browsers (like Netscape~4.5)
are unhappy about \textsc{post} using this method.
\end{AttrDecl}

\begin{AttrDecl}{legend\_example\_size}
Sets the length of the example line in the legend. Defaults to 20.
\end{AttrDecl}

