@c CfgTie --> Environment manager
@c Copyright 1998-1999, Randall Maas.  All rights reserved.  This program is
@c free software; you can redistribute it and/or modify it under the same terms
@c as PERL itself.                                                                   
@chapter CfgTie:: A Configuration Interface thru Perl
@heading Introduction

CfgTie is a package of Perl modules and tools.  These make it easier to
configure and maintain Unix computers.

The idea is that just about everything in your machines environment can --
nay should -- be operable thru a single consistent interface.  This is a
set of tools that make many of the various configuration subsystem in your
machine appear to be Perl variables of some sort.  (There are other modules
available from CPAN for the other aspects of your environment).

@subheading Problem Domain
This module makes the configuration text files and subsystems available to
Perl as conventional objects.  These are mapped into Perl, usually as hash
arrays, but providing object methods where appropriate.  Any changes to these
is mapped back into the various text files and other subsystems.

@subheading Installation
After unpacking the tar file, do:
@example
        perl Makefile.PL 
        make 
        make test
        make install
@end example

@subheading Additional, post-install tests
There are some extra tests that can also be done after a successful install.
This are not intended for normal installs, but for developpers working on
CfgTie and various extensions.

@subheading Optional Modules
@itemize @bullet
@item Rcs
@item Getopts::Long
@end itemize

@subheading How to find out more
@table @emph
@item online documentation
There is a set of online documentation.
@url{http://www.geocities.com/CapeCanaveral/Lab/1862/script/CfgTie_toc.html}

@item mailling list
There is a mailling list to discuss this package.

@table @asis
@item Send email to @email{cfgtie@@onelist.com}
@item You can subscribe by going to
@url{http://www.onelist.com/subscribe.cgi/cfgtie}
@item You can browse through the archives by going to
 @url{http://www.onelist.com/archives.cgi/cfgtie}

@item You can subscribe by going to OneList's homepage.
 @url{http://www.onelist.com/}

@end table

@item Contact the author:
Randall Maas (@email{randym@@acm.org})
@end table

@subheading Copyright

Copyright @copyright{} 1998-1999, Randall Maas. All rights reserved.  This
package is free software; you can redistribute it and/or modify it
under the same terms as Perl itself.

@node Overview, SS, Introduction, Top
@include docs/Overview.tex

@node SS, CSS, Overview, Top
@include docs/Security.tex

@node CSS, Modules, SS, Top
@include docs/CSS.tex

@c --- Configuration --------------------------------------------------------
@node Modules, Related Work, CSS, Top
@chapter Modules

@c nodes it should add: by type, all
@c right now I am going to have by category

@menu

* bykind::

* bytype::

* alphabetical::

@end menu

@node bykind, bytype, Modules, Modules
@section Modules, by kind

@menu

* Examples:: Example utilities

* Network::  Network related configuration

* Users::    Users, Groups, etc. Stuff

@end menu

@c Add a way to look at the code by sections
@c Start-up stuff
@c Email stuff
@c Servicer stuff
@c Client Stuff


@node Examples, Network, bykind, bykind
@section Examples
@menu

* CfgAliases:: A Command Line Tool to manage @file{/etc/aliases}

* CfgNamed:: A Command line tool to manage your DNS server

* mail-validate:: A tool that describes possible problems with the mail spool

* sys.cgi :: A CGI script to browse thru the configuration

@end menu

@node Network, Users, Examples, bykind
@section Network

@menu

* CfgNamed::	

* CfgTie-TieHost::	

* CfgTie-TieNamed::	

* CfgTie-TieNet::	

* CfgTie-TieProto::	

* CfgTie-TieServ::	

@end menu

@node Users, , Network, bykind
@section User and Group Configuration

@menu

* CfgTie-TieGroup::

* CfgTie-TieShadow::

* CfgTie-TieUser:: 

@end menu

@include CfgTie2.tex


@node Related Work, Revisions, Modules, Top
@include docs/Related.tex


@node Revisions, Function Index, Related Work, Top
@unnumbered File Revisions
@menu

* Files bykind::

* Files bytype::

* Files alphabetical::

@end menu

@node Files bykind, Files bytype, Revisions, Revisions
@unnumbered Files bykind

@include CfgTie-revs.tex

