\chapter{Begin}


\hyperdef{amuse}{label}{}%
\hyperdef{amuse}{label1}{}%
Here the doc start
here blablabla
A simple internal link is created with \textbackslash{}hypertarget, with two parameters of an anchor name, and anchor text. \textbackslash{}hyperlink has two arguments, the name of a hypertext object defined somewhere by \textbackslash{}hypertarget, and the text which be used as the link on the page.

\chapter{Middle}


\hyperdef{amuse}{label2x}{}%
\hyperdef{amuse}{label2}{}%
\hyperdef{amuse}{label3}{}%
\#label2 Continue here
A simple internal link is created with \textbackslash{}hypertarget, with two parameters of an anchor name, and anchor text. \textbackslash{}hyperlink has two arguments, the name of a hypertext object defined somewhere by \textbackslash{}hypertarget, and the text which be used as the link on the page.
A simple internal link is created with \textbackslash{}hypertarget, with two parameters of an anchor name, and anchor text. \textbackslash{}hyperlink has two arguments, the name of a hypertext object defined somewhere by \textbackslash{}hypertarget, and the text which be used as the link on the page.
A simple internal link is created with \textbackslash{}hypertarget, with two parameters of an anchor name, and anchor text. \textbackslash{}hyperlink has two arguments, the name of a hypertext object defined somewhere by \textbackslash{}hypertarget, and the text which be used as the link on the page.
 \#label3 is a label

\chapter{Next}


\hyperdef{amuse}{label2}{}%
This is valid.


\#1blabla
Not a label, starts with a number


\begin{alltt}
\#label3
This is verbatim
\end{alltt}



\begin{quote}


\hyperdef{amuse}{label5}{}%
in quotation is not neutralized,



\end{quote}



\begin{verse}
\#label6 \\{}
in verse is not neutralized
\end{verse}

\hyperdef{amuse}{label7}{}%


\begin{verse}
~in verse again, we have a label
\end{verse}


\hyperdef{amuse}{label9}{}%
This is a label despite of the trailing whitespace.


\hyperdef{amuse}{label9}{}%
This is a label despite of the leading whitespace.


\begin{enumerate}[1.]
\item\relax 
\#label8 not a label



\item\relax 
\#lable9
This is a not label



\item\relax 
\hyperdef{amuse}{label3enum}{}%
This \emph{is} a label




\end{enumerate}
\chapter{End}


Here we \hyperref{}{amuse}{label}{go} and \hyperref{}{amuse}{label2}{label2} and \hyperref{}{amuse}{label3}{dead link} \hyperref{}{amuse}{label4}{label4}
\href{\#1}{Preserved verbatim}
\href{\#label2\%20unkown}{\texttt{\#label2 unkown}}
\hyperref{}{amuse}{label}{\textbackslash{}tryme}

