@c CfgTie --> Environment manager
@c Copyright 1998-1999, Randall Maas.  All rights reserved.  This program is
@c free software; you can redistribute it and/or modify it under the same terms
@c as PERL itself.                                                                   
@chapter Related Work and things to do

@heading Related Modules
The following is a table of related modules.  They are different from this
module.  Any feedback or work on determining if this difference should be
reduced would be appreciated.  Of course, doing the work too.

@table @asis
@item HTTPD
There is a Perl module, @code{HTTPD-Tools} that help configure the HTTPD
daemon.

@item .newsrc associative array
The Perl module that already does this is @code{News-Newsrc}

@item Process associative arrays
@c open "ps -awxhjch|"; ppid,pid,pgid,sid,tty,tpgid, stat,uid, time, command
@c if tty not equal to '?'
The relevant existing Perl module is @code{Proc-ProcessTable}.
If it used an associative array interface, in part, this would make
signalling named services easier.

@item Quotas
The relevant Perl module is @code{Quota}
The quota subsystem works with the C<CfgTie::TieUser> and the
C<CfgTie::TieMTab> hash-spaces.

@item Windows INI files
The relevenat Perl module is @code{Win32_Tie_Ini_Source}

@item Windows Registry Files
The relevant Perl module is @code{Win32_TieRegistry}
@end table

@heading What needs to be or could be written
@table @asis
@item Get tested on Win32 platforms
@item Get tested on Qube platforms
@item Get tested on Solaris platforms
@item Get tested on MacPerl platforms
@item Ability to add or remove a service from various run levels
@item Ability to add or remove a service altogether
@item Ability to change the defaults for a service
@item IO descriptor associative array
manipulate sockets and files and such

@item semaphore associative array

@item shared memory associative array

@item arp interface

@item session associative array

@item tty associative array

@item folder associate array
Scan folders and such.  Not necessarily good idea.

@end table

The future:
@table @asis 
@item Boundaries, routers, gateways and bridges
@itemize @bullet
@item ascend
@item cisco
@end itemize

@item Interlink services
@itemize @bullet
@item sendmail
@item qmail
@item apache
(see the HTTPD thing above.)
@item INN
@item modifying services table (media protocols, and service protocols)
@end itemize

@item Monitor services
@itemize @bullet
@item NOCOL
@item statusd
@end itemize

@item Distribution services
@itemize @bullet
@item rsync, rdist
@end itemize

@item User interfaces
@itemize @bullet
@item XWindows
 Window managers (FVWM2)
 .Xresources
@item C shell
@item POSIXly shells --  Korn & Bourne & BASH
@end itemize

@item Local system
@itemize @bullet
@item filesystem tables
@item tunefs
@end itemize

@item Ability to receive batch changes
@item CVS
@item Handle symbolic links better.
@item Work with cfengine
@url{http://www.delorie.com/gnu/docs/cfengine/}

@item Possibly work with RFC 2244
@url{ftp://ftp.isi.edu/in-notes/rfc2244.txt}

@item Work with linuxconf
@url{http://www.solucorp.qc.ca/linuxconf/}
@item Work with webmin
@url{http://www.webmin.com/webmin/}
@item Possibly work with opStore
@url{http://24.1.97.22/gmd/opStore/framedIndex.html}
@end table

