\section{NAME\label{NAME}\index{NAME}}


Net::Hulu - Perl extension for the Net::Hulu name space.  Can be use to download
and process all XML-formatted RSS feeds provided by the popular site hulu.com.

\section{ABSTRACT\label{ABSTRACT}\index{ABSTRACT}}


Net::Hulu will download and process XML-formatted RSS feeds provided by hulu.com.

\section{SYNOPSIS\label{SYNOPSIS}\index{SYNOPSIS}}
\begin{verbatim}
  use strict;
  use warnings;
  use Net::Hulu qw(
                get_recent_videos get_recent_shows get_recent_movies get_highest_rated_videos
                get_popular_videos_today get_popular_videos_this_week get_popular_videos_all_time
                get_soon_to_expire_videos get_recent_blog_postings download_recent_videos_xml
                download_recent_shows_xml download_recent_movies_xml download_highest_rated_videos_xml
                download_popular_videos_today_xml download_popular_videos_this_week_xml
                download_popular_videos_all_time_xml download_soon_to_expire_videos_xml
                download_recent_blog_postings_xml get_popular_videos_this_month
                download_popular_videos_this_month_xml);
\end{verbatim}
\section{DESCRIPTION\label{DESCRIPTION}\index{DESCRIPTION}}


Net::Hulu provides methods to download all XML-formatted RSS feeds provided by hulu.com and 
then return a data structure to the user containing the Data from the RSS feeds.



The following methods will download RSS feeds from hulu.com to directory where Hulu.pm is installed.
Method download\_recent\_videos\_xml will download RSS feed for recent videos.
Method download\_recent\_shows\_xml will download RSS feed for recent shows.
Method download\_recent\_movies\_xml will download RSS feed for recent movies.
Method download\_highest\_rated\_videos\_xml will download RSS feed for highest rated videos.
Method download\_popular\_videos\_today\_xml will download RSS feed for today's popular videos.
Method download\_popular\_videos\_this\_week\_xml will download RSS feed for this week's popular videos.
Method download\_popular\_videos\_this\_month\_xml will download RSS feed for this month's popular videos.
Method download\_popular\_videos\_all\_time\_xml will download RSS feed for most popular videos of all time.
Method download\_soon\_to\_expire\_videos\_xml will download RSS feed for soon to expire videos.
Method download\_recent\_blog\_postings\_xml will download RSS feed for recent blog postings to hulu.com.



The following methods will process all RSS feeds provided by hulu.com.
Method get\_recent\_videos returns a list of recently added videos to the user.
Method get\_recent\_shows returns a list of recently added shows to the user.
Method get\_recent\_movies returns a list of recently added movies to the user.
Method get\_highest\_rated\_videos returns a list of highest rated videos to the user.
Method get\_popular\_videos\_today returns a list of most popular videos today to the user.
Method get\_popular\_videos\_this\_week returns a list of most popular videos this week to the user.
Method get\_popular\_videos\_this\_month returns a list of most popular videos this month to the user.
Nethod get\_popular\_videos\_all\_time returns a list of most popular videos of all time to the user.
Method get\_soon\_to\_expire\_videos returns a list of soon to expire videos to the user.
Method get\_recent\_blog\_postings returns recent blog postings for hulu.com to the user.

\subsection*{Getting Started\label{Getting_Started}\index{Getting Started}}


The following code will download all the XML-formatted RSS feeds provided by hulu.com,
process their content, and print the results for the user.

\begin{verbatim}
   use strict;
   use warnings;
   use Net::Hulu qw(
                   get_recent_videos get_recent_shows get_recent_movies get_highest_rated_videos
                   get_popular_videos_today get_popular_videos_this_week get_popular_videos_all_time
                   get_soon_to_expire_videos get_recent_blog_postings download_recent_videos_xml
                   download_recent_shows_xml download_recent_movies_xml download_highest_rated_videos_xml
                   download_popular_videos_today_xml download_popular_videos_this_week_xml
                   download_popular_videos_all_time_xml download_soon_to_expire_videos_xml
                   download_recent_blog_postings_xml);
\end{verbatim}
\begin{verbatim}
   download_recent_videos_xml();
   get_recent_videos();
\end{verbatim}
\begin{verbatim}
   download_recent_shows_xml();
   get_recent_shows();
\end{verbatim}
\begin{verbatim}
   download_recent_movies_xml();
   get_recent_movies();
\end{verbatim}
\begin{verbatim}
   download_highest_rated_videos_xml();
   get_highest_rated_videos();
\end{verbatim}
\begin{verbatim}
   download_popular_videos_today_xml();
   get_popular_videos_today();
\end{verbatim}
\begin{verbatim}
   download_popular_videos_this_week_xml();
   get_popular_videos_this_week();
\end{verbatim}
\begin{verbatim}
   download_popular_videos_this_month_xml();
   get_popular_videos_this_month();
\end{verbatim}
\begin{verbatim}
   download_popular_videos_all_time_xml();
   get_popular_videos_all_time();
\end{verbatim}
\begin{verbatim}
   download_soon_to_expire_videos_xml();
   get_soon_to_expire_videos();
\end{verbatim}
\begin{verbatim}
   download_recent_blog_postings_xml();
   get_recent_blog_postings();
\end{verbatim}
\subsection*{download\_recent\_videos\_xml\label{download_recent_videos_xml}\index{download\ recent\ videos\ xml}}


The subroutine download\_recent\_videos\_xml will download http://rss.hulu.com/HuluRecentlyAddedVideos?format=xml
to the directory where Hulu.pm is installed.

\subsection*{get\_recent\_videos\label{get_recent_videos}\index{get\ recent\ videos}}


The subroutine get\_recent\_videos will return a list of recently added videos for the user.

\subsection*{download\_recent\_shows\_xml\label{download_recent_shows_xml}\index{download\ recent\ shows\ xml}}


The subroutine download\_recent\_shows\_xml will download http://rss.hulu.com/HuluRecentlyAddedShows?format=xml
to the directory where Hulu.pm is installed.

\subsection*{get\_recent\_shows\label{get_recent_shows}\index{get\ recent\ shows}}


The subroutine get\_recent\_shows will return a list of recently added shows for the user.

\subsection*{download\_recent\_movies\_xml\label{download_recent_movies_xml}\index{download\ recent\ movies\ xml}}


The subroutine download\_recent\_movies\_xml will download http://rss.hulu.com/HuluRecentlyAddedMovies?format=xml
to the directory where Hulu.pm is installed.

\subsection*{get\_recent\_movies\label{get_recent_movies}\index{get\ recent\ movies}}


The subroutine get\_recent\_movies will return a list of recently added movies for the user.

\subsection*{download\_highest\_rated\_videos\_xml\label{download_highest_rated_videos_xml}\index{download\ highest\ rated\ videos\ xml}}


The subroutine download\_highest\_rated\_videos\_xml will download http://www.hulu.com/feed/highest\_rated/videos
to the directory where Hulu.pm is installed.

\subsection*{get\_highest\_rated\_videos\label{get_highest_rated_videos}\index{get\ highest\ rated\ videos}}


The subroutine get\_highest\_rated\_videso will return a list of the highest rated videos for the user.

\subsection*{download\_popular\_videos\_today\_xml\label{download_popular_videos_today_xml}\index{download\ popular\ videos\ today\ xml}}


The subroutine download\_popular\_videos\_today\_xml will download http://rss.hulu.com/HuluPopularVideosToday?format=xml
to the directory where Hulu.pm is installed.

\subsection*{get\_popular\_videos\_today\label{get_popular_videos_today}\index{get\ popular\ videos\ today}}


The subroutine get\_popular\_videos\_today will return a list of the most popular videos today for the user.

\subsection*{download\_popular\_videos\_this\_week\_xml\label{download_popular_videos_this_week_xml}\index{download\ popular\ videos\ this\ week\ xml}}


The subroutine download\_popular\_videos\_this\_week\_xml will download http://rss.hulu.com/HuluPopularVideosThisWeek?format=xml
to the directory where Hulu.pm is installed.

\subsection*{get\_popular\_videos\_this\_week\label{get_popular_videos_this_week}\index{get\ popular\ videos\ this\ week}}


The subroutine get\_popular\_videos\_this\_week will return a list of most popular videos this week for the user.

\subsection*{download\_popular\_videos\_this\_month\_xml\label{download_popular_videos_this_month_xml}\index{download\ popular\ videos\ this\ month\ xml}}


The subroutine get\_popular\_videos\_this\_month\_xml will download http://rss.hulu.com/HuluPopularVideosThisMonth?format=xml
to the directory where Hulu.pm is installed.

\subsection*{get\_popular\_videos\_this\_month\label{get_popular_videos_this_month}\index{get\ popular\ videos\ this\ month}}


The subroutine get\_popular\_videos\_this\_month will return a list of most popular videos this month for the user.

\subsection*{download\_popular\_videos\_all\_time\_xml\label{download_popular_videos_all_time_xml}\index{download\ popular\ videos\ all\ time\ xml}}


The subroutine download\_popular\_videos\_all\_time\_xml will download http://rss.hulu.com/HuluPopularVideosAllTime?format=xml
to the directory where Hulu.pm is installed.

\subsection*{get\_popular\_videos\_all\_time\label{get_popular_videos_all_time}\index{get\ popular\ videos\ all\ time}}


The subroutine get\_popular\_videos\_all\_time will return a list of most popular videos of all time to the user.

\subsection*{download\_soon\_to\_expire\_videos\_xml\label{download_soon_to_expire_videos_xml}\index{download\ soon\ to\ expire\ videos\ xml}}


The subroutine download\_soon\_to\_expire\_videos\_xml will download http://www.hulu.com/feed/expiring/videos
to the directory where Hulu.pm is installed.

\subsection*{get\_soon\_to\_expire\_videos\label{get_soon_to_expire_videos}\index{get\ soon\ to\ expire\ videos}}


The subroutine get\_soon\_to\_expire\_videos will return a list of soon to expire videos to the user.

\subsection*{download\_recent\_blog\_postings\_xml\label{download_recent_blog_postings_xml}\index{download\ recent\ blog\ postings\ xml}}


The subroutine download\_recent\_blog\_postings\_xml will download http://rss.hulu.com/HuluBlog?format=xml
to the directory where Hulu.pm is installed.

\subsection*{get\_recent\_blog\_postings\label{get_recent_blog_postings}\index{get\ recent\ blog\ postings}}


The subroutine get\_recent\_blog\_postings will return a list of blog postings to hulu.com to the user.

\subsection*{SEE ALSO\label{SEE_ALSO}\index{SEE ALSO}}


Please see the documentation for the Perl modules XML::Twig an LWP::Simple
for details on how Net::Hulu downloads and processes the XML-formatted
RSS feeds provided by the popular website hulu.com.



Please send all bug reports to the maintainer's email address hevenerg \{[at]\} marshall \{[dot]\} edu.

\section{AUTHOR\label{AUTHOR}\index{AUTHOR}}


Net::Hulu was written and is currently maintained by Gerald L. Hevener, M.S..

\section{COPYRIGHT AND LICENSE\label{COPYRIGHT_AND_LICENSE}\index{COPYRIGHT AND LICENSE}}


Copyright (C) 2009 by Gerald L. Hevener, M.S. $<$hevenerg \{[at]\} marshall \{[dot]\} edu.



This library is free software; you can redistribute it and/or modify
it under the same terms as Perl itself, either Perl version 5.10.1 or,
at your option, any later version of Perl 5 you may have available.

\section{DISCLAIMER OF WARRENTY\label{DISCLAIMER_OF_WARRENTY}\index{DISCLAIMER OF WARRENTY}}


BECAUSE THIS SOFTWARE IS LICENSED FREE OF CHARGE, THERE IS NO WARRANTY FOR THE SOFTWARE, TO THE EXTENT PERMITTED BY APPLICABLE LAW. EXCEPT WHEN OTHERWISE STATED IN WRITING THE COPYRIGHT HOLDERS AND/OR OTHER PARTIES PROVIDE THE SOFTWARE "AS IS" WITHOUT WARRANTY OF ANY KIND, EITHER EXPRESSED OR IMPLIED, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE. THE ENTIRE RISK AS TO THE QUALITY AND PERFORMANCE OF THE SOFTWARE IS WITH YOU. SHOULD THE SOFTWARE PROVE DEFECTIVE, YOU ASSUME THE COST OF ALL NECESSARY SERVICING, REPAIR, OR CORRECTION.



IN NO EVENT UNLESS REQUIRED BY APPLICABLE LAW OR AGREED TO IN WRITING WILL ANY COPYRIGHT HOLDER, OR ANY OTHER PARTY WHO MAY MODIFY AND/OR REDISTRIBUTE THE SOFTWARE AS PERMITTED BY THE ABOVE LICENCE, BE LIABLE TO YOU FOR DAMAGES, INCLUDING ANY GENERAL, SPECIAL, INCIDENTAL, OR CONSEQUENTIAL DAMAGES ARISING OUT OF THE USE OR INABILITY TO USE THE SOFTWARE (INCLUDING BUT NOT LIMITED TO LOSS OF DATA OR DATA BEING RENDERED INACCURATE OR LOSSES SUSTAINED BY YOU OR THIRD PARTIESOR A FAILURE OF THE SOFTWARE TO OPERATE WITH ANY OTHER SOFTWARE), EVEN IF SUCH HOLDER OR OTHER PARTY HAS BEEN ADVISED OF THE POSSIBILITY OF SUCH DAMAGES.
=cut

